Cassini State Capture

### 2019-08-29 initial/notes.tex
fix sign mistake, problem 3 looks good
fix algebra on P3/4 Phops, now look really good

\textbf{Note:} The full formula, by actually evaluating all the terms, comes out
to be
\begin{equation}
    P_{hop} = \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi
        \p{1 - 2\eta \sin I - \eta^2 \cos^2 I}
        + 8\eta^{3/2}\cos I \sqrt{\sin I}}.
\end{equation}
It bears noting this formula slightly overpredicts $P_{hop}$ compared to the
actual simulation values; this comes down to ICs too near the separatrix being
necessarily escape-bound (can see \autoref{fig:CS4s} for more evidence).

@@

For clarity, $H$ and $H_4$ are now
\begin{align*}
    H &= -\frac{\mu^2}{2}
            + \eta\p*{\mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi}, &
    H_4 &= -\eta \sin I + \frac{\eta^2 \cos^2 I}{2}.
\end{align*}
Thus, our $B_i$ are
\begin{align*}
    B_i &= \int_{\mathcal{C}_i} \epsilon \mu \eta
            \s*{-\sin I + \eta \cos^2 I -
                \p*{\mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi}}
            \;\mathrm{d}t,\\
        &\approx \int_{\mathcal{C}_i} \epsilon \mu \eta
            \frac{\eta \cos^2 I - \mu \cos I
                + \sin I\p*{\cos \phi \sqrt{1 - \mu^2} - 1}}{-\mu + \eta \cos I}
            \;\mathrm{d}\phi,\\
        &= \int_{\mathcal{C}_i} \epsilon \mu \eta
            \p*{-\cos I + \sin I \frac{\cos \phi \sqrt{1 - \mu^2} - 1}{-\mu +
            \eta \cos I}} \;\mathrm{d}\phi.
\end{align*}
That the second term does not diverge requires some careful work:
\begin{align*}
    \frac{\cos \phi\sqrt{1 - \mu^2} - 1}{\mu - \eta \cos I}
        &\approx \frac{\sqrt{1 - 2\eta \sin I\p*{1 - \cos \phi}}\cos \phi
            - 1}{\mu - \eta \cos I},\\
        &\approx \frac{(1 - \eta \sin I(1 - \cos \phi))\cos \phi - 1}{
            \mu - \eta \cos I},\\
        &\approx \pm\frac{(1 + \eta \sin I)(\cos \phi - 1)}{\sqrt{2\eta \sin I
            (1 - \cos \phi)}},\\
        &\approx \mp\sqrt{\frac{1 - \cos \phi}{2\eta \sin I}},\\
    B_i &= \int_{\mathcal{C}_i} \epsilon \mu \eta
            \p*{-\cos I \pm \sin I
                \sqrt{\frac{1 - \cos \phi}{2\eta \sin I}}} \;\mathrm{d}\phi.
\end{align*}
Note that the plus sign corresponds to the top integral, where $\mu - \eta \cos
I > 0$. The top integral evaluates easily
\begin{align*}
    B_{top} &= \int\limits_{2\pi}^0 -\epsilon \mu \eta \cos I\;\mathrm{d}\phi
            + \frac{\epsilon}{2}\int\limits_{2\pi}^0
                \mu\sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi,\\
        &= \epsilon \eta \cos I\p*{2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
            + \frac{\epsilon}{2}\p*{\eta \cos I (8\sqrt{\eta \sin I})
            + 4\pi \eta \sin I},\\
        &= \epsilon \eta \s*{
            2\pi \sin I + 12\sqrt{\eta \sin I}\cos I + 2\pi \eta \cos^2 I}.
\end{align*}
The bottom integral just flips the signs of the cross terms (the $\sqrt{\eta}$
terms), since the integration path changes, which changes the sign inside the
$B_i$ expression and $\mu$. The total integral is the difference between the top
and bottom integrals, which is just twice the sign-changed terms, and so we
obtain
\begin{equation}
    P_c = \frac{24\cos I \sqrt{\eta \sin I}}{
            2\pi \sin I + 12\sqrt{\eta \sin I}\cos I + 2\pi \eta \cos^2 I}.
\end{equation}
Indeed we get the same expression; this is probably since the approximations we
made in writing down $B_i$ washed out the extra $\eta$ dependence.

For reference, let's also write down the $B_i$ in the $\dot{\eta} = \epsilon
\eta$ case. First, $B_{+}$:
\begin{align*}
    B_{top} &= \int\limits_{2\pi}^0 -\epsilon \eta \cos I\;\mathrm{d}\phi
            + \frac{\epsilon}{2}\int\limits_{2\pi}^0
                \sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi,\\
        &= 2\pi \epsilon \eta \cos I - \frac{\epsilon}{2}8\sqrt{\eta \sin I}.
\end{align*}
Along the bottom leg, the first term changes signs (both integrals have their
paths flipped, but the sign of the second integral also changes), and so
\begin{equation}
    B_{\pm} = \pm 2\pi \epsilon \eta \cos I
        - \frac{\epsilon}{2}8\sqrt{\eta \sin I}.
\end{equation}
Generally, since $\eta$ is small, $B_{+} + B_- < -\abs*{B_+}, -\abs*{B_-}$ which
implies guaranteed capture from both sides, as expected (note that in our actual
paper, we compute changes for $h \equiv H^{(0)} - H_4$, while here we compute
changes in $H_4 - H^{(0)}$, accounting for the change in sign).

@@

We can now compute the $\Delta_{\pm}$ changes in $h \equiv H^{(0)} - H_4$
(following my paper's convention, rather than those earlier in these notes),
which are:
\begin{equation}
    \Delta_{\pm} = \epsilon\s*{\mp 2\pi \p{1 - 2\eta \sin I - \eta^2 \cos^2 I} +
        16\cos I\eta^{3/2}\sqrt{\sin I}} + f\epsilon
            \s*{\mp 2\pi \eta \cos I + 4\sqrt{\eta \sin I}}.
\end{equation}
The two contributions are bracketed.

@@

\textbf{Revisited:} We should be able to evaluate this integral analytically.
We've already mostly done the $\dot{\mu}\;\mathrm{d}\phi$ integral, let's now
consider the $\frac{\dot{s}}{\dot{\phi}}\Delta H_{,s}\;\mathrm{d}\phi$
component. This is just (we change sign convention, $\Delta H = H - H_4$ now,
per recent developments)
\begin{align*}
    \int_{\mathcal{C}_{\pm}} \frac{\dot{s}}{\dot{\phi}^{(0)}}
            \pd{\Delta H}{s}\;\mathrm{d}\phi &=
        \int \dot{s}\frac{-\frac{\mu^2}{2s_c} + \frac{\cos^2 Is_c}{2s^2}}{
            -\frac{s}{s_c}\mu + \cos I}\;\mathrm{d}\phi,\\
        &= \int \frac{\dot{s}s_c}{2s^2}\s*{\frac{s\mu}{s_c} + \cos
            I}\;\mathrm{d}\phi,\\
        &= \pm \int \epsilon 2\Omega_1
            \p*{\mu_{\pm} - \frac{s}{2\Omega_1}\p*{1 + \mu_{\pm}^2}}
                \frac{s_c}{2s^2} \sqrt{2\frac{s_c}{s} \sin I\p*{1 - \cos \phi}}
                \;\mathrm{d}\phi,\\
        &\approx \pm \frac{\epsilon \Omega_1 s_c}{s^2}
            \int \p*{\mu_{\pm} - \frac{s}{2\Omega_1}}
            \sqrt{2\frac{s_c}{s} \sin I\p*{1 - \cos \phi}} \;\mathrm{d}\phi,\\
        &\approx \pm\frac{\epsilon \Omega_1 s_c}{s^2}
            \int \p*{\mu_4 - \frac{s}{2\Omega_1} \pm
                \sqrt{2\frac{s_c}{s} \sin I\p*{1 - \cos \phi}}}
            \sqrt{2\frac{s_c}{s} \sin I\p*{1 - \cos \phi}} \;\mathrm{d}\phi,\\
        &= \frac{\epsilon \Omega_1 s_c}{s^2}\s*{
            \pm \p*{\mu_4 - \frac{s}{2\Omega_1}}\p*{-8\sqrt{\eta \sin I}}
                + 4\pi \frac{s_c}{s}\sin I}.
\end{align*}
Indeed, the sum over the two legs is positive, which is expected: during
spindown, the separatrix expands, so the separatrix must have $\Delta H > 0$
owing just to adiabatic expansion.

For the $\dot{\mu}$ integral, the integrand is $\p*{\frac{2\Omega}{s} - \mu}$
times the original integrand; this means the final result is $\frac{2\Omega}{s}$
times the old result plus a contribution approximately $-\int \epsilon \mu
\;\mathrm{d}\phi$. This latter term is a purely antisymmetric contribution, so
we may approximate
\begin{align*}
    \int_{\mathcal{C}_{\pm}}\dot{\mu}^{(1)}\;\mathrm{d}\phi
        &\approx \epsilon\frac{2\Omega}{s}\p{\mp 2\pi
            + 16\cos I \eta^{3/2}\sqrt{\sin I}}
            + 8\epsilon\sqrt{\eta \sin I},\\
        &\approx \mp \frac{4\pi\epsilon \Omega}{s} + 8\sqrt{\eta \sin I}.
\end{align*}
This is in agreement with our work from 5.1. Thus, the total expression is

>>>>

\textbf{Note:} The full formula, by actually evaluating all the terms, comes out
to be
\begin{equation}
    P_{hop} = \frac{16\eta^{3/2}\cos I \sqrt{\sin I}}{\pi
        \p*{1 - 2\eta \sin I - \eta^2 \cos^2 I}
        + 8\eta^{3/2}\cos I \sqrt{\sin I}}.
\end{equation}
It bears noting this formula slightly overpredicts $P_{hop}$ compared to the
actual simulation values; this comes down to ICs too near the separatrix being
necessarily escape-bound (can see \autoref{fig:CS4s} for more evidence).

@@

For clarity, $H$ and $H_4$ are now
\begin{align*}
    H &= -\frac{\mu^2}{2}
            + \eta\p*{\mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi}, &
    H_4 &= -\eta \sin I + \frac{\eta^2 \cos^2 I}{2}.
\end{align*}
Thus, our $B_i$ are
\begin{align*}
    B_i &= \int_{\mathcal{C}_i} \epsilon \mu \eta
            \s*{-\sin I + \eta \cos^2 I -
                \p*{\mu \cos I - \sin I \sqrt{1 - \mu^2}\cos \phi}}
            \;\mathrm{d}t,\\
        &\approx \int_{\mathcal{C}_i} \epsilon \mu \eta
            \frac{\eta \cos^2 I - \mu \cos I
                + \sin I\p*{\cos \phi \sqrt{1 - \mu^2} - 1}}{-\mu + \eta \cos I}
            \;\mathrm{d}\phi,\\
        &= \int_{\mathcal{C}_i} \epsilon \mu \eta
            \p*{\cos I + \sin I \frac{\cos \phi \sqrt{1 - \mu^2} - 1}{-\mu +
            \eta \cos I}} \;\mathrm{d}\phi.
\end{align*}
That the second term does not diverge requires some careful work:
\begin{align*}
    \frac{\cos \phi\sqrt{1 - \mu^2} - 1}{\mu - \eta \cos I}
        &\approx \frac{\sqrt{1 - 2\eta \sin I\p*{1 - \cos \phi}}\cos \phi
            - 1}{\mu - \eta \cos I},\\
        &\approx \frac{(1 - \eta \sin I(1 - \cos \phi))\cos \phi - 1}{
            \mu - \eta \cos I},\\
        &\approx \pm\frac{(1 + \eta \sin I)(\cos \phi - 1)}{\sqrt{2\eta \sin I
            (1 - \cos \phi)}},\\
        &\approx \mp\sqrt{\frac{1 - \cos \phi}{2\eta \sin I}},\\
    B_i &= \int_{\mathcal{C}_i} \epsilon \mu \eta
            \p*{\cos I \pm \sin I
                \sqrt{\frac{1 - \cos \phi}{2\eta \sin I}}} \;\mathrm{d}\phi.
\end{align*}
Note that the plus sign corresponds to the top integral, where $\mu - \eta \cos
I > 0$. The top integral evaluates easily
\begin{align*}
    B_{top} &= \int\limits_{2\pi}^0 \epsilon \mu \eta \cos I\;\mathrm{d}\phi
            + \frac{\epsilon}{2}\int\limits_{2\pi}^0
                \mu\sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi,\\
        &= -\epsilon \eta \cos I\p*{2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
            - \frac{\epsilon}{2}\p*{\eta \cos I (8\sqrt{\eta \sin I})
            + 4\pi \eta \sin I},\\
        &= -\epsilon \eta \s*{
            2\pi \sin I + 12\sqrt{\eta \sin I}\cos I + 2\pi \eta \cos^2 I}.
\end{align*}
The bottom integral just flips the signs of the cross terms (the $\sqrt{\eta}$
terms), since the integration path changes, which changes the sign inside the
$B_i$ expression and $\mu$. The total integral is the difference between the top
and bottom integrals, which is just twice the sign-changed terms, and so we
obtain
\begin{equation}
    P_c = \frac{24\cos I \sqrt{\eta \sin I}}{
            2\pi \sin I + 12\sqrt{\eta \sin I}\cos I + 2\pi \eta \cos^2 I}.
\end{equation}
Indeed we get the same expression; this is probably since the approximations we
made in writing down $B_i$ washed out the extra $\eta$ dependence.

For reference, let's also write down the $B_i$ in the $\dot{\eta} = \epsilon
\eta$ case. First, $B_{+}$:
\begin{align*}
    B_{top} &= \int\limits_{2\pi}^0 \epsilon \eta \cos I\;\mathrm{d}\phi
            + \frac{\epsilon}{2}\int\limits_{2\pi}^0
                \sqrt{2\eta \sin I\p*{1 - \cos \phi}}\;\mathrm{d}\phi,\\
        &= -2\pi \epsilon \eta \cos I - \frac{\epsilon}{2}8\sqrt{\eta \sin I}.
\end{align*}
Along the bottom leg, the first term changes signs (both integrals have their
paths flipped, but the sign of the second integral also changes), and so
\begin{equation}
    B_{\pm} = \mp 2\pi \epsilon \eta \cos I
        - \frac{\epsilon}{2}8\sqrt{\eta \sin I}.
\end{equation}
Generally, since $\eta$ is small, $B_{+} + B_- < -\abs*{B_+}, -\abs*{B_-}$ which
implies guaranteed capture from both sides, as expected (note that in our actual
paper, we compute changes for $h \equiv H^{(0)} - H_4$, while here we compute
changes in $H_4 - H^{(0)}$, accounting for the change in sign).

@@

We can now compute the $\Delta_{\pm}$ changes in $h \equiv H^{(0)} - H_4$
(following my paper's convention, rather than those earlier in these notes),
which are:
\begin{equation}
    \Delta_{\pm} = \epsilon\s*{\mp 2\pi \p*{1 - 2\eta \sin I - \eta^2 \cos^2 I} +
        16\cos I\eta^{3/2}\sqrt{\sin I}} + f\epsilon
            \s*{\pm 2\pi \eta \cos I + 4\sqrt{\eta \sin I}}.
\end{equation}
The two contributions are bracketed.

@@

\textbf{Revisited:} We should be able to evaluate this integral analytically.
We've already mostly done the $\dot{\mu}\;\mathrm{d}\phi$ integral, let's now
consider the $\frac{\dot{s}}{\dot{\phi}}\Delta H_{,s}\;\mathrm{d}\phi$
component. This is just (we change sign convention, $\Delta H = H - H_4$ now,
per recent developments)
\begin{align*}
    \int_{\mathcal{C}_{\pm}} \frac{\dot{s}}{\dot{\phi}^{(0)}}
            \pd{\Delta H}{s}\;\mathrm{d}\phi &=
        \int \dot{s}\frac{-\frac{\mu^2}{2s_c} + \frac{\cos^2 Is_c}{2s^2}}{
            -\frac{s}{s_c}\mu + \cos I}\;\mathrm{d}\phi,\\
        &= \int \frac{\dot{s}s_c}{2s^2}\s*{\frac{s\mu}{s_c} + \cos
            I}\;\mathrm{d}\phi,\\
        &= \int \epsilon 2\Omega_1
            \p*{\mu_{\pm} - \frac{s}{2\Omega_1}\p*{1 + \mu_{\pm}^2}}
                \frac{s_c}{2s^2} \s*{
                    2\cos I \pm
                    \sqrt{2\frac{s}{s_c} \sin I\p*{1 - \cos \phi}}}
                \;\mathrm{d}\phi,\\
        &\approx \epsilon \frac{s_c}{s^2} \int
            \p*{\mu_{\pm} - \frac{s}{2}}
                \s*{2\cos I \pm \sqrt{\frac{2 \sin I}{\eta}\p*{1 - \cos \phi}}}
                \;\mathrm{d}\phi.
\end{align*}
At this point, the integral is rather messy, so we have approximated $1 +
\mu_{\pm}^2 \approx 1$, set $\epsilon = \Omega_1 = 1$, then split $\mu_{\pm} -
s/2$ into two terms, $\mu_4 - s/2$ and the square root. We further break down
into three terms to evaluate the integral of the product: the $2\cos I$ term,
the product of the two square root components. These three integrals are
respectively
\begin{align*}
    \int_{\pm} 2\cos I \p*{\mu_{\pm} - \frac{s}{2}}\;\mathrm{d}\phi &=
        -2\cos I\p*{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
        \pm 2\pi s\cos I,\\
    \pm \int_{\pm} \p*{\mu_4 - \frac{s}{2}}
            \sqrt{\frac{2\sin I}{\eta}\p*{1 - \cos \phi}} \;\mathrm{d}\phi &=
        \eta \cos I \p*{-8\sqrt{\sin I / \eta}}
            + \frac{s}{2}8\sqrt{\sin I/\eta} ,\\
    \int_{\pm} 2\sin I \p*{1 - \cos \phi}\;\mathrm{d}\phi &= \mp 4\pi \sin I.
\end{align*}

Indeed, the sum over the two legs is positive, which is expected: during
spindown, the separatrix expands, so the separatrix must have $\Delta H > 0$
owing just to adiabatic expansion.

For the $\dot{\mu}$ integral, the integrand is $\p*{\frac{2\Omega}{s} - \mu}$
times the original integrand; this means the final result is $\frac{2\Omega}{s}$
times the old result plus a contribution $\int \epsilon \p*{1 - \mu^2}\p*{-\mu}
\;\mathrm{d}\phi$. This second term can be evaluated exactly, and we obtain
\begin{align*}
    \int_{\mathcal{C}_{\pm}}\dot{\mu}^{(1)}\;\mathrm{d}\phi
        &\approx \epsilon\frac{2\Omega}{s}\p*{\mp 2\pi\p*{1 - 2\eta \sin I}
            + 16\cos I \eta^{3/2}\sqrt{\sin I}}
            + 8\epsilon\sqrt{\eta \sin I}
            \pm 2 \pi \eta \cos I
            - \frac{64}{3}\epsilon \p*{\eta \sin I}^{3/2}.
\end{align*}
This is in agreement with our work from 5.1. Thus, the total expression is
\begin{align}
    \frac{\Delta_{\pm}}{\epsilon} ={}&
        -2\cos I\p*{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
        \pm 2\pi s\cos I
        + \eta \cos I \p*{-8\sqrt{\sin I / \eta}}
            + \frac{s}{2}8\sqrt{\sin I/\eta}\nonumber\\
        &+ \frac{2\Omega}{s}\p*{\mp 2\pi\p*{1 - 2\eta \sin I}
            + 16\cos I \eta^{3/2}\sqrt{\sin I}}
            + 8\sqrt{\eta \sin I}
            \pm 2 \pi \eta \cos I
            - \frac{64}{3} \p*{\eta \sin I}^{3/2},\\
    P_c ={}& \frac{\Delta_+ + \Delta_-}{\Delta_-}.
\end{align}

### 2019-08-29 writeups/Su_sep_cross.tex
fix algebra on P3/4 Phops, now look really good

The accuracy of \autoref{eq:p3_p_c} is illustrated in \autoref{fig:p3_hist}. A
small deviation can be noticed at larger $\eta_\star$ values as $f$ is
increased. This is attributed to the separatrix becoming significantly
asymmetric around $\eta \sim 0.15$, therefore our \autoref{eq:mu_sep} is no
longer an accurate approximation. When $f = 0$, the small deviations are
significantly suppressed as the numerator scales with $\eta_\star^{3/2}$
compared to when $f \sim 1$, where the numerator instead scales with
$\eta_{\star}^{1/2}$.
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{../initial/3_toy3/1hist20_0_00.png}
        \caption{$\delta/\epsilon = 0$}
    \end{subfigure}

@@

    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{../initial/3_toy3/1hist20_0_70.png}
        \caption{$\delta/\epsilon = 0.7$}
    \end{subfigure}
    \caption{Histogram of simulation and inferred $P_c(s_\star)$ compared with
    \autoref{eq:p3_p_c}, where $f = \delta/\epsilon$ is varied. $3 \times 10^4$
    initial conditions were used for both plots. While the $f = 0$ case
    indicates perfect agreement, the other two cases show increasingly large
    deviations at larger $\eta_\star$.}\label{fig:p3_hist}
\end{figure}

@@

Note that here $s$ takes the role of adiabatically-varying parameter. Thus, when
computing $\Delta_{\pm}$ along the separatrix using \autoref{eq:delta}, there
are two contributions. In particular, we write
\begin{equation}
    \Delta_{\pm} = \int_{\mathcal{C}_{\pm}} \dot{\mu}^{(1)} +
        \frac{\dot{s}}{\dot{\phi}^{(0)}} \pd{h}{s}
        \;\mathrm{d}\phi.
\end{equation}
Both of these integrals were performed in preceeding sections, and we may
express in closed form (dropping some terms for simplicity)
\begin{align}
    \Delta_{\pm} \approx{}& \epsilon\z{
            \mp \frac{4\pi  \Omega_1}{s} + 8\sqrt{\frac{s_c}{s}\sin I}
            }\nonumber\\
        &+\epsilon\z{\frac{ \Omega_1 s_c}{s^2}
            \s{\pm 8\sqrt{\frac{s_c}{s} \sin I}
            \p{\frac{s}{2\Omega_1} - \frac{s_c\cos I}{s}}
                + 4\pi \frac{s_c}{s}\sin I}}.\label{eq:delta_p4}
\end{align}
We can then compute separatrix capture probability from zone III (which is $P_c
= \frac{\Delta_+ + \Delta_-}{\Delta_-}$), again evaluating at $s = s_\star$:
\begin{equation}
    P_c(s_\star) = \frac{16\sqrt{\frac{s_c}{s_\star}\sin I} +
        8\pi\frac{s_c}{s_\star}\sin I}{
            \frac{4\pi \Omega_1}{s_\star} - \frac{8\Omega_1
            s_c}{s_\star^2}\sqrt{\frac{s_c}{s_\star}\sin I}
            \p{\frac{s_\star}{2\Omega_1} - \frac{s_c \cos I}{s_\star}}}.
            \label{eq:p_c_p4}
\end{equation}
Note that for $\frac{s_c}{s_\star} < \eta_c$ that no separatrix (or resonance)
exists anymore, so we will generally assume $s_\star \gtrsim s_c, \Omega_1$.

To test \autoref{eq:p_c_p4}, we generate an evenly spaced grid of initial
conditions $(\mu_0, \phi_0)$ and initialize $s_0 = 10$. We then record $s_\star$
and the final outcome of the trajectory over many simulations. The agreement of
\autoref{eq:p_c_p4} with data can be observed in \autoref{fig:1_4stats}.
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/1_weaktide/4_cross_hist0_05.png}
    \end{subfigure}

@@

    \caption{Histogram of simulation and inferred $P_c(s_\star)$ compared with
    \autoref{eq:p_c_p4}. $s_c$ used are numbered at the top of each plot. $10^4$
    simulations were used for each plot, and a single $I = 20^\circ$ was
    used.}\label{fig:1_4stats}
\end{figure}

>>>>

The good accuracy of \autoref{eq:p3_p_c} is illustrated in
\autoref{fig:p3_hist}. Both a red line from \autoref{eq:p3_p_c} and a black line
from numerically evaluating $\Delta h$ along the numerically-determined
separatrix (obtained by solving $H(\mu_{sep}, \phi_{sep}) = H_4$) are presented.
Good agreement is observed.
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{../initial/3_toy3/1hist20_0_00.png}
        \caption{$\delta/\epsilon = 0$}
    \end{subfigure}

@@

    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\textwidth]{../initial/3_toy3/1hist20_0_70.png}
        \caption{$\delta/\epsilon = 0.7$}
    \end{subfigure}
    \caption{Histogram of simulation and inferred $P_c(s_\star)$ compared with
    \autoref{eq:p3_p_c}, where $f = \delta/\epsilon$ is varied. $3 \times 10^4$
    initial conditions were used for both plots. The solid red line denotes the
    prediction of \autoref{eq:p3_p_c}, while the black dotted line is estimated
    via numerical integration instead.}\label{fig:p3_hist}
\end{figure}

@@

Note that here $s$ takes the role of adiabatically-varying parameter. Thus, when
computing $\Delta_{\pm}$ along the separatrix using \autoref{eq:delta}, there
are two contributions. In particular, we write
\begin{equation}
    \Delta_{\pm} = \int_{\mathcal{C}_{\pm}} \dot{\mu}^{(1)} +
        \frac{\dot{s}}{\dot{\phi}^{(0)}} \pd{h}{s}
        \;\mathrm{d}\phi.
\end{equation}
Both of these integrals were performed in preceeding sections, and we may
express in closed form (dropping some terms for simplicity)
\begin{align}
    \frac{\Delta_{\pm}}{\epsilon} ={}&
        -2\cos I\p*{\pm 2\pi \eta \cos I + 8\sqrt{\eta \sin I}}
        \pm 2\pi s\cos I\nonumber\\
        &+ \eta \cos I \p*{-8\sqrt{\sin I / \eta}}
            + \frac{s}{2}8\sqrt{\sin I/\eta}\nonumber\\
        &+ \frac{2\Omega}{s}\p*{\mp 2\pi\p*{1 - 2\eta \sin I}
            + 16\cos I \eta^{3/2}\sqrt{\sin I}}\nonumber\\
        &+ 8\sqrt{\eta \sin I}
            \pm 2 \pi \eta \cos I
            - \frac{64}{3} \p*{\eta \sin I}^{3/2},\label{eq:delta_p4}\\
    P_{c} &= \frac{\Delta_+ + \Delta_-}{\Delta_-}. \label{eq:p_c_p4}
\end{align}
Here, $P_c$ describes the separatrix capture probability from zone III\@. Note
that for $\frac{s_c}{s_\star} < \eta_c$ that no separatrix (or resonance) exists
anymore, so we will generally assume $s_\star \gtrsim s_c$ and correspeondingly
$\Omega_1$.

To test \autoref{eq:p_c_p4}, we generate an evenly spaced grid of initial
conditions $(\mu_0, \phi_0)$ and initialize $s_0 = 10$. We then record $s_\star$
and the final outcome of the trajectory over many simulations. The agreement of
\autoref{eq:p_c_p4} with data can be observed in \autoref{fig:1_4stats}. As
before, a red solid line depicting \autoref{eq:p_c_p4} and a black dotted line
using numerical evaluation of $\Delta h$ and a numerically-determined separatrix
are depicted.
\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{../initial/1_weaktide/4_cross_hist0_05.png}
    \end{subfigure}

@@

    \caption{Histogram of simulation and inferred $P_c(s_\star)$ compared with
    \autoref{eq:p_c_p4}. $s_c$ used are numbered at the top of each plot. $10^4$
    simulations were used for each plot, and a single $I = 20^\circ$ was
    used. The solid red and dotted black lines denote N\autoref{eq:p_c_p4} and a
    full numerical evaluation of $P_c$ from $\Delta_{\pm}$ respectively. Note
    that small values of $s$ cannot be evaluated as the separatrix has
    disappeared $\eta > \eta_c$.}\label{fig:1_4stats}
\end{figure}
